\RequirePackage{pdfmanagement-testphase} \DocumentMetadata{}
\documentclass[11pt]{article}%
\usepackage{color}%
\usepackage{amsmath}%
\setcounter{MaxMatrixCols}{30}%
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{graphicx}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage{enumitem}

\usepackage{tagpdf}
\tagpdfsetup{uncompress, %for the test, to check the pdf
             activate-mc}

\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}

\renewcommand{\baselinestretch}{1.1}
\topmargin=-1.0in
\footskip=10pt
\textheight=10in
\textwidth=6.5in
\oddsidemargin=0in
\pagestyle{plain}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
}

\newdateformat{mydate}{\THEMONTH/\THEDAY/\THEYEAR}

\begin{document}
\begin{center}
{\Large \textsc{Eric H. Weisbrod}} \\
\textit{Curriculum Vit\ae }\\[0pt]\phantom{bosluk}
\begin{tabular*}
{6.5in}[c]{l@{\extracolsep{\fill}}r}%
University\ of Kansas & Phone : (785) 864-1868\\
School\ of Business Adminstration & Email: \textcolor {blue}{eric.weisbrod@ku.edu} \\
1654 Naismith Drive &  \href{https://business.ku.edu/eric-weisbrod}{https://business.ku.edu/eric-weisbrod}\\
Lawrence, Kansas 66045 &  \href{https://www.linkedin.com/in/eric-weisbrod}{https://www.linkedin.com/in/eric-weisbrod}\\

\end{tabular*}

%THIS IS WHERE I UPDATE THE DATE
\rule[-3mm]{5.50in}{0.9mm} \raisebox{-3mm}{\tiny {\textit{updated
\mydate\today}}} \rule[1mm]{6.5in}{0.1mm}


\end{center}


\subsubsection*{\textit{Academic Positions Held\\[-4mm] \protect\rule[0.1mm]{6.5in}{0.1mm}}}
\begin{tabular*}
{6.5in}[c]{l@{\extracolsep{\fill}}r}%
University of Kansas, School of Business  & Lawrence, KS\\
Associate Professor of Accounting (with tenure), 2023 - Present  \\
Assistant Professor of Accounting, 2020 - 2023 \bigskip & \\

University of Miami, Miami Herbert Business School  & Coral Gables, FL\\
Assistant Professor of Accounting, 2012 - 2020 \bigskip & \\

U.S. Securities and Exchange Commission, Office of the Chief Accountant & Washington, DC\\
Academic Fellow, August 2016 - July 2017 &\\
\end{tabular*}


\subsubsection*{\textit{Education\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}
\begin{tabular*}
{6.5in}[c]{l@{\extracolsep{\fill}}r}%
Arizona State University, W.P. Carey School of Business & Tempe, AZ\\
Ph.D. in Accounting, May 2012\bigskip & \\
Claremont McKenna College & Claremont, CA\\
B.A. in Economics-Accounting with Computer Science Sequence, May 2005 & \\
\textit{Cum Laude, Honors in Major} &
\end{tabular*}


\subsubsection*{\textit{Publications and Accepted Manuscripts\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}
%\textbf{}
\begin{enumerate}
\item Easton, P., Kapons, M., Monahan, S., Sch\"utt, H., and E. Weisbrod, 2024. Forecasting Earnings Using k-Nearest Neighbors. \textbf{\textit{The Accounting Review}}, 99(3): 115-140. 
\item Bochkay, K., Markov, S., Subasi, M., and E. Weisbrod, 2022. The Roles of Data Providers and Analysts in the Production, Dissemination, and Pricing of Street Earnings. \textbf{\textit{Journal of Accounting Research}}, 60: 1695-1740.
\item Weisbrod, E. 2019. Stockholders' Unrealized Returns and the Market Reaction to Financial Disclosures. \textbf{\textit{The Journal of Finance}}, 74: 899-942.  
\item Bianchi, P., D. Falsetta, M. Minutti-Meza, and E. Weisbrod, 2019. Joint Audit Engagements and Client Tax Avoidance: Evidence from the Italian Statutory Audit Regime. \textbf{\textit{Journal of the American Taxation Association}}, 41(1): 31-58. 
	\vspace*{-0.1in} 
	\begin{itemize}
	    \item \textit{Best Paper Award: 2015 AAA International Section Midyear Meeting}
	\end{itemize}
\item Akbas, F., S. Markov, M. Subasi, and E. Weisbrod, 2018. Determinants and Consequences of Information Processing Delay: Evidence from Thomson Reuters' Institutional Brokers’ Estimate System. \textbf{\textit{Journal of Financial Economics}}, 127: 366-388. 

\end{enumerate}

\newpage
\noindent \subsubsection*{\textit{Publications and Accepted Manuscripts (Continued)\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}
\begin{enumerate}[resume*]
\item Dhaliwal, D., S. Kaplan, R. Laux, and E. Weisbrod, 2013. The Information Content of Tax Expense for Firms Reporting Losses, \textbf{\textit{Journal of Accounting Research,}} 51 (1): 135-164. 
\item Weisbrod, E. 2009. The role of affect and tolerance of ambiguity in ethical decision making. \textbf{\textit{Advances in Accounting,}} 25(1), 57-63.
\end{enumerate}

\subsubsection*{\textit{Working Papers\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}	
%\textbf{Working Papers}
\begin{itemize}
	\item Consensus? An Examination of Differences in Earnings Information Across Forecast Data Providers. Revising for 3rd round review at \textit{Journal of Accounting Research}. (with S. Larocque and J. Watkins). 

	\item Social Media Discussion of Sell-Side Analyst Research: Evidence from Twitter. Under 2nd round review at \textit{Review of Accounting Studies}. (with A. Call, M. Kara, and M. Peterson). 
    
 	\item Plaintiff's Attorney Marketing as a Signal of Corporate Litigation Risk. (with S. Kaplan, A. Masli, and M. Peterson). 
	
 	\item Top Down vs. Bottom Up Index Forecasts: Are Market Strategists Strategically Pessimistic? (with M. Park and M. Peterson). 
\end{itemize}
% \subsubsection*{\textit{Work in Progress\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}	
% %\textbf{Work in Progress}
% \begin{itemize}

% 	\item Game On? The Effect of Trading Platform Gamification on Investors' Risk-Taking. (with W. Bazley and A. Winn). 
	

	
% \end{itemize}
% \textbf{Other Research}
% \begin{itemize}
% 	\item Weisbrod, E. (2009). \textquotedblleft The role of affect and tolerance of ambiguity in ethical decision making.\textquotedblright\ \textit{Advances in Accounting,} 25(1), 57-63.
% \end{itemize}
\subsubsection*{\textit{Invited Presentations and Discussions\\[-6mm]\protect\rule[-1.5mm]{6.5in}{0.1mm}}}
\textbf{2025:} Hawaii Accounting Research Conference (Honolulu, HI), AAA FARS PhD Consortium, FARS Midyear Meeting (Atlanta, GA), University of Arkansas (Bentonville, AR), AAA Deloitte Foundation PhD Consortium (Dallas, TX) \newline
\textbf{2024:} Hawaii Accounting Research Conference (Honolulu, HI), AAA FARS Midyear Meeting (Denver, CO), AAA ATA Midyear Meeting (Long Beach, CA), AAA Annual Meeting (Washington, DC) \newline
\textbf{2023:} AAA FARS Midyear Meeting (Phoenix, AZ), AAA ATA Midyear Meeting (Washington, DC), Arizona State University, Kansas State University, AAA Annual Meeting (Denver, CO) \newline
\textbf{2022:} AAA FARS Midyear Meeting (Virtual), Columbia Accounting Design Project (Virtual) \newline
\textbf{2021:} AAA FARS Midyear Meeting (Virtual), EAA Annual Congress (Virtual) \newline
\textbf{2020:} AAA FARS Midyear Meeting (Nashville, TN) \newline
\textbf{2019:} Hawaii Accounting Research Conference (Honolulu, HI), AAA FARS Midyear Meeting (Seattle, WA), Florida Accounting Symposium (Gainseville, FL), University of California - Riverside (Riverside, CA), Washington University (St. Louis, MO), CFEA Conference (New York, NY), Dartmouth College (Dartmouth, NH), University of Houston (Houston, TX), University of Kansas (Lawrence, KS), CUNY Baruch (New York, NY), University of Utah (Salt Lake City, UT), American University (Washington, DC) \newline
\textbf{2018:} RAST Conference Discussant (South Bend, IN), Southern Methodist University, Penn State University, AAA Annual Meeting (Nat. Harbor, MD), Erasmus University (Rotterdam, Netherlands) \newline
\textbf{2017:} SEC Division of Economic and Risk Analysis (Washington, DC), Georgetown University (Washington, DC)\newline
\textbf{2016:} AAA ATA Midyear Meeting (Orlando, FL),  International Symposium on Audit Research (Singapore), University of Maryland - College Park\newline

\newpage
\subsubsection*{\textit{Invited Presentations and Discussions (Continued) \\[-6mm]\protect\rule[-1.5mm]{6.5in}{0.1mm}}}

\textbf{2010 - 2015:} University of Texas - Dallas, AAA ATA Midyear Meeting (Washington, DC),  Southern Methodist University, EAA Annual Congress (Glasgow, Scotland), International Symposium on Audit Research (Boston, MA), Florida Accounting Symposium (Gainseville, FL), University of Illinois - Chicago, University of Miami, University of Colorado - Boulder, AAA FARS Midyear Meeting (Houston, TX), University of Miami, JATA Conference (San Diego, CA), Arizona State University, South Florida Accounting Research Conference (Miami, FL), University of Texas - Dallas, London Business School, University of Miami, Singapore Management University, Georgia State University, NYU Stern, University of
Missouri, University of Arizona, Arizona State University, AAA Annual Meeting (San Francisco, CA), Arizona State University

% \subsubsection*{\textit{Conference Participation\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}
% \textbf{2019:} AAA/Deloitte Foundation Trueblood Seminar (Westlake, TX), PwC Analytics Academy (Rosemont, IL), CARE Conference (Leesburg, VA), GSU CEAR Conference (Atlanta, GA), Wash. U Dopuch Conference (St. Louis, MO) \newline
% \textbf{2018:} FARS Midyear Meeting (Austin, TX), CARE Conference (Leesburg, VA) \newline
% \textbf{2017:} Washington Area Research Conference (Washington, DC), JAPP Conference (College Park, MD) \newline
% \textbf{2016:} ATA Midyear Meeting (Orlando, FL), International Symposium on Audit Research (Singapore), CARE Conference (Leesburg, VA), AAA Annual Meeting (New York, NY), PCAOB/JAR Conference (Washington, D.C.)  \newline
% \textbf{2015:} Florida Accounting Symposium (Gainseville, FL), University of Illinois-Chicago Accounting Conference, AAA Annual Meeting (Chicago, IL), Northwestern Causal Inferences Workshop, EAA Annual Congress (Glasgow, Scotland), AAA ATA Section Midyear Meeting (Washington, DC), AAA Auditing Section Midyear Meeting (Miami, FL)     \newline
% \textbf{2014:} University of Miami Behavioral Finance Conference, University of Miami International Financial Reporting Conference, Florida Accounting Symposium (Coral Gables, FL), Deloitte Foundation/FSA Faculty Consortium (Westlake, TX), Penn State Accounting Research Conference, AAA Annual Meeting (Atlanta, GA), AAA FARS Midyear Meeting (Houston, TX)  \newline
% \textbf{2013:} AAA New Faculty Consortium (Leesburg, VA), AAA ATA Mid-Year Meeting (San Diego, CA), UNC Tax Symposium\newline
% \textbf{2007 - 2012:} 2012 AAA FARS Mid-Year Meeting (Chicago, IL), 2010 AAA Annual Meeting (San Francisco, CA), 2010 J. Michael Cook Doctoral Consortium (Lake Tahoe, CA), 2009 PAC-10 Plus Doctoral Consortium (Boulder, CO), 2008 AAA FARS Mid-year Meeting (Phoenix, AZ), 2007 RAST Conference (Tempe, AZ)

\subsubsection*{\textit{Teaching\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}
University of Kansas\newline%
\vspace*{-0.3in} 
\begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-0.08in}
\item ACCT 721, Advanced Financial Accounting (MAcc) [Fall 2020, Spring 2022 - 2025]
\item ACCT 932, Seminar in Financial Accounting Research (PhD) [Fall 2022, 2024]
\item ACCT 995, Seminar in Applied Business Research (PhD) [Spring 2025]
\end{list}
University of Miami\newline%
\vspace*{-0.3in} 
\begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-0.08in}
\item ACC 672, Advanced Financial Analysis and Valuation [Fall 2017, 2018, 2019]
\item ACC 670, Financial Reporting \& Analysis (MBA) [Fall 2017]
\item ACC 311, Intermediate Financial Accounting I [Fall 2012, 2013, 2014, 2015]
\item Recipient: School of Business Excellence in Undergraduate Teaching Award, 2013-14
\end{list}
Arizona State University\newline%
\vspace*{-0.3in} \begin{list}{\labelitemi}{\leftmargin=1em \itemsep=-0.08in}
\item ACC 241, Introductory Managerial Accounting [Summer 2010]
\item ACC 231, Introductory Financial Accounting [Summer 2008]
\end{list}
\subsubsection*{\textit{Honors, Awards, and Fellowships\\[-4mm]%
\protect\rule[0.1mm]{6.5in}{0.1mm}}}
Best Reviewer Award, Hawaii Accounting Research Conference, 2025 \newline
Best Paper Award, AAA International Section Midyear Meeting, 2015 \newline
Provost's Research Award in Busines and	Social Sciences, University of Miami, 2013, 2014\newline
J. Hal Reneau Memorial Fellowship, Arizona State University, 2011\newline AAA/Deloitte/J. Michael Cook
Doctoral Consortium Fellow, 2010\newline California Society of CPAs Doctoral
Scholarship, 2010 - 2012\newline Arizona State University, University Graduate
Fellowship for Outstanding Achievement on Doctoral Comprehensive Exam,
2009\newline Arizona State University, Outstanding Doctoral Student
Fellowship, 2008, 2009, 2010, 2011\newline Financial Executives International,
Los Angeles Chapter, Outstanding Scholar Award, 2004
\newpage
\subsubsection*{\textit{Service\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}
Ad-hoc Reviewer, \textit{The Accounting Review}, \textit{Review of Accounting Studies}, \textit{Contemporary Accounting Research}, \textit{Management Science}, \textit{Journal of Forensic \& Investigative Accounting}\newline
AAA Distinguished Contribution to Accounting Literature Committee 2024 - Present \newline
FARS Integrating Research and Practice Committee, 2025\newline
FARS Mentoring Committee, 2024-2025 \newline
ATA Midyear Meeting Planning Committee, 2025, 2026 \newline
AAA Doctoral Consortium Planning Committee 2024 - Present\newline
KU University Libraries Committee, 2024 - Present \newline
KU School of Business Reseach Database Committee, 2020 - Present \newline
AAA FARS Best Dissertation Award Committee, 2022 \newline
Track Chair, FARS AAA Annual Meeting, 2021 \newline
Reviewer, AAA FARS Mid-Year Meeting \newline
Reviewer, Conference for Financial Economics and Accounting \newline
Reviewer, Hawaii Accounting Research Conference \newline
Member, Miami Business School Research Database Advisory Committee, 2017 - 2020 \newline
Member, EAA Scientific Committee 2016, 2017, 2024 \newline
Member, Miami Business School Undergraduate Academic Integrity Taskforce, 2014 - 2016 \newline
Reviewer, AAA Auditing Section Mid-Year Meeting \newline
ATA New Faculty Concerns Committee, 2013 \newline
Guest Lecturer, Two Week SAS/STATA PhD Programming Bootcamp, 2010, 2011
\newline Founder and Organizer, ASU\ Financial Accounting Reading Group, 2010-2011\newline



\subsubsection*{\textit{Professional Experience\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}%
\begin{tabular*}
{6.5in}[c]{l@{\extracolsep{\fill}}r}%
\textbf{Cornerstone Research} & Los Angeles, CA\\
Analyst, 2005 - 2007 & \vspace*{0.2in}\\
\textbf{Certified Public Accountant} & \\
California, 2008 - Present (Inactive) &
\end{tabular*}
% \subsubsection*{\textit{References\\[-4mm]\protect\rule[0.1mm]{6.5in}{0.1mm}}}%
% \begin{tabular*}
% {6.5in}[c]{l@{\extracolsep{\fill}}r}%
% Peter Easton & Stanimir Markov\\
% Notre Dame Alumni Professor of Accountancy & Ashbel Smith Professor, Accounting \\
% University of Notre Dame & University of Texas-Dallas \\
%  peaston@nd.edu & stan.markov@utdallas.edu\\
%   574-631-6096 & 972-883-5166\\
%  & \\
% Steve Kaplan & Stephen Hillegeist\\
% KPMG Professor & Associate Professor \\
% Arizona State University & Arizona State University \\
%  Steve.Kaplan@asu.edu & Stephen.Hillegeist@asu.edu\\
%   480-965-6498 & 480-965-6216 \\
%  & \\
% Diana Falsetta & \\
% Associate Professor & \\
% Miami Business School & \\
% falsetta@miami.edu & \\
% 305-284-8642 &  \\

\end{document}